NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-30 aaV_main.tex
cern preprint number
minor updates in text

\affiliation[a]{Physik Institut, Universit{\"a}t Z{\"u}rich, Winterthurerstr.190, 8057 Z\"urich, Switzerland}
\affiliation[b]{CERN}

\preprint{
  \small
  \begin{flushright}
    ZU--TH--??, CERN-- 
  \end{flushright}
}

\abstract{
Processes with three external electroweak gauge boson allow for a measurement of triple and quartic gauge
couplings. They allow for a constraint of anomalous gauge couplings, where new physics might predominantly
couple to electroweak gauge bosons. In this paper we chose a class of such processes where we consider two photons
and an additional vector boson in the final state. As additional vector boson we consider either a third photon or a
$W$ or $Z$ boson. For the latter two cases we assume a leptonic decay of the boson. We calculate the next-to-leading
order QCD and electroweak corrections to these processes with a particular emphasize on the until now unknown 
electroweak corrections. We find that the electroweak corrections to the total cross section are moderate in the range of a few 
per cent at most, but can reach several tens of per cent in regions of phase space  that are particularly interesting
 in the context of new physics searches. In addition we investigate the difference between additive and multiplicative scheme 
 when combining
QCD and electroweak corrections and we asess the importance of photon induced contributions to these processes. 
}

>>>>

\affiliation[a]{Physik Institut, Universit{\"a}t Z{\"u}rich, Winterthurerstr.190, 8057 Z\"urich, Switzerland}
\affiliation[b]{Theoretical Physics Department, CERN, 1211 Geneva 23, Switzerland}

\preprint{
  \small
  \begin{flushright}
    ZU--TH--??\\ CERN-TH-2017-226
  \end{flushright}
}

\abstract{
Processes with three external electroweak gauge boson allow for a measurement of triple and quartic gauge
couplings. They can be used to constrain anomalous gauge couplings, where new physics might predominantly
couple to electroweak gauge bosons. In this paper we chose a class of such processes where we consider two photons
and an additional vector boson in the final state. As additional vector boson we consider either a third photon or a
$W$ or $Z$ boson. For the latter two cases we assume a leptonic decay of the boson. We calculate the next-to-leading
order QCD and electroweak corrections to these processes with a particular emphasize on the until now unknown 
electroweak corrections. We find that the electroweak corrections to the total cross section are moderate in the range of a few 
per cent at most, but can reach several tens of per cent in regions of phase space  that are particularly interesting
 in the context of new physics searches. In addition we investigate the difference between additive and multiplicative scheme 
 when combining
QCD and electroweak corrections and we asess the importance of photon induced contributions to these processes. 
}
